### 2018-09-14 manuscript.tex
Update manuscript.tex

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.  This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test the three theories aforementioned. \jd{This P. seems insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.}

@@

There are two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires \jd{``Certain questions'' sounds weaselly. Also, it's not clear we need to talk about MICS; using DHS seems very reasonable.} only available in DHS.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 09/17).

Only women \jd{What does this mean: with daughters to be considered} for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\jd{We need to know how DHS decided who to ask the question.}
\cf{Explain how we choose women}

@@

\jd{Is this s. about us or not? Why is it in our Methods?} The main constructs analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to perform the behavior (or not); and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  Here, we refer the attitudes to women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control to perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and to their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory). \cf{need comments!!!} \jd{Not sure what you're trying to do here. What do you mean by ``refer''? Seems loose.}

@@

>>>>

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.  This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.} \cf{good point. reframed and may still need more thoughts.}

@@

We analyzed the Demographic and Health Surveys (DHS) by USAID.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 09/17).

Only women with daughters to be considered for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\jd{We need to know how DHS decided who to ask the question.}
\cf{Explain how we choose women}

@@

\jd{Is this s. about us or not? Why is it in our Methods?} The main constructs analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Here, the attitudes is constructed as women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control as perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory). \cf{need comments!!!} \jd{Not sure what you're trying to do here. What do you mean by ``refer''? Seems loose.}

@@

\cf{Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to perform the behavior (or not); and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.}
